Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-21 paper.tex
Pass on background

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), as a way to
teach a robot an action policy while interacting based on a supervisor
correcting actions about to be executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment associated to the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action based on which previously identified
features are currently in the environment and submit it to its supervisor.

@@

Classic approaches in RL generally rely on exploring virtual environments where the agent
tries to maximise the reward. In many cases where RL achieves success, the agent
had access to a virtual environment where the only real cost of exploring was 
time and energy, and the agent can interact as long as needed to gather
enough information on the environment to find a correct action policy. When
these conditions are reunited, RL can achieve impressive results, as shown by
the victory of a computer in Backgammon back in the
90s~\cite{tesauro1995temporal} or more recently the success achieved in playing
Atari games based only on the image and the game rewards~\cite{mnih2015human}.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be use in the designing of the algorithm, the
representation of the state and actions spaces and the rewrd funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitive rather than raw motor angles or adding additional
informations in the reward function have important impacts on the ability of
the robot to reach a successful policy.

@@

These demonstrations can also be used to learn a reward function. With Inverse
Reinforcement Learning, the agent is not provided with a reward function, but
derives it from a set of expert demonstrations. The agent can then explore
around the demonstrated policy to find how to optimise the reward function. With
this approach, Abbeel and Ng achieved better than human control for a robotic
helicopter~\cite{abbeel2004apprenticeship}.

\subsubsection{Guiding the learning:}

In some cases, the state space is simply too big to rely only on random exploration to
reach a successful action policy.Rather than solely providing initial knowledge
to the agents, humans can also guide the agent throughout the learning in a more
human-like teaching manner.

A first approach consists in sequencing tasks the robot will face. 
This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
increase the difficulty and complexity of the task or the environment as the
robot is learning policies to achieve complex task not directly learnable in the final
environment.

A second approach is "shaping". For example, the TAMER framework
\cite{knox2009interactively}, allows to teach an agent an action policy in an
environment providing no rewards using a human observer to supply rewards to the
agent. With this approach the teacher can adapt the
rewards to the current policy and performance of the agent, for example starting to reward
positively suboptimal behaviours but which still improve the current policy and
later, as the agent improve its behaviour reward these same suboptimal behaviour
negatively and only the optimal ones positively.

Another approach to guide the the learning is to bias the action selection.
In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
supply  an agent both rewards and potential guidance or advise indicating where
the agent should pay attention, or what it should do next. And they show that
giving the power to the supervisor to bias the action selection can improve the
learning, making it faster, safer.

In \cite{senft2015sparc}, we introduced the Supervised Progressively
Autonomous Robot Competencies (SPARC). SPARC relies on the presence of a
supervisor teaching a robot how to interact in an environment. This teacher
knowns which actions the robot is about to execute and can cancel an action or
select another to be executed. Based on the supervisor's decisions, the robot
learns which actions are desired and can refine its policy over time reducing
the need for the teacher to correct or select an action.

@@

In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
assigning a positive reward to every action executed by the robot as it would
have been explicitely or implicitely approved by the supervisor. However this method
was not making use of any kind of generalisation, directly mapping a
single (state,action) pair to a reward, and as such is not applicable to
environments with a continuous or high dimensional space or undeterministic
transition from one state to another.

>>>>

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
teach a robot an action policy while interacting based on a supervisor
correcting actions about to be executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment associated to the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action based on which previously identified
features are currently in the environment and submit it to its supervisor.

@@

Classic approaches in RL generally rely on exploring virtual environments where the agent
tries to maximise the reward. In many cases where RL achieves success, the agent
has access to a virtual environment where the only real cost of exploring is 
time and energy, and the agent can interact as long as needed to gather
enough information on the environment to find a correct action policy. When
these conditions are reunited, RL can achieve impressive results, as shown by
the victory of a computer in Backgammon back in the
90s~\cite{tesauro1995temporal} or more recently the success mastering the game
of go~\cite{silver2016mastering}.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be use in the designing of the algorithm, the
representation of the state and actions spaces and the reward funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitive rather than raw motor angles or adding additional
informations in the reward function have important impacts on the ability of
the robot to reach a successful policy~\cite{kober2013reinforcement}.

@@

These demonstrations can also be used to learn a reward function. With Inverse
Reinforcement Learning, the agent is not provided with a reward function, but
derives it from a set of expert demonstrations. The agent can then explore
around the demonstrated policy to find how to optimise the reward function. With
this approach, Abbeel and Ng achieved better than human control for a robotic
helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts.

\subsubsection{Guiding the learning:}
Rather than solely providing initial knowledge
to the agents, humans can also guide the agent throughout the learning in a more
human-like teaching manner.

A first approach consists in sequencing tasks the robot will face. 
This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
increase the difficulty and complexity of the task as the robot is learning
reaching policies not directly learnable in the final environment.

A second approach is "shaping". For example, the TAMER framework
\cite{knox2009interactively}, allows to teach an agent an action policy in an
environment providing no rewards using a human observer to supply rewards to the
agent. With this approach the teacher can adapt the
rewards to the current policy and performance of the agent, for example starting to reward
positively suboptimal behaviours but better than the current policy and
later, as the agent improve its behaviour, reward these same suboptimal
behaviours negatively and only the optimal ones positively.

Another approach to guide the the learning is to bias the action selection.
In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
supply  an agent both rewards and potential guidance or advise indicating where
the agent should pay attention, or what it should do next. They show that
giving the power to the supervisor to bias the action selection can improve the
learning, making it faster and safer.

In \cite{senft2015sparc}, we introduced the Supervised Progressively
Autonomous Robot Competencies (SPARC). SPARC relies on supervisor with the
ability to control the robot's actions. This teacher is presented with the
actions the robot is about to execute and can cancel an action, let it be
executed or select another to be executed. Based on the supervisor's decisions,
the robot learns which actions are desired and can refine its policy over time
reducing the need for the teacher to correct or select an action.

@@

In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
assigning a positive reward to every action executed by the robot as it would
have been explicitely or implicitely approved by the supervisor. However this method
was not making use of any kind of generalisation, directly mapping a
single (state, action) pair to a reward, and as such is not applicable to
environments with a continuous or high dimensional space or undeterministic
transition from one state to another.
